% DOCUMENT CLASS
\documentclass[12pt]{article}


% LINGUISTIC EXAMPLES
\usepackage{gb4e}
\noautomath
\let\eachwordone=\it % italicize transcriptions
\def\glt{\nobreak\vskip.17\baselineskip} % keep glosses on same page
\medskip


% PARALLEL GLOSSES
\usepackage{parcolumns} % parallel columns
\usepackage{enumitem} % needed to number columns

\newcounter{parnum} % counter for paragraphs in texts
\newcounter{textID}\addtocounter{textID}{1} % unique text ID counter

% command for Arabic transcription with automatic label
\newcommand{\parabic}[1]{\colchunk{\begin{itemize}[leftmargin=*] \item[\leavevmode\refstepcounter{parnum}\arabic{parnum}]{\textit{#1}\label{\currentsecno-par\arabic{parnum}}}%
    \end{itemize}}}
    
% command for English gloss
\newcommand{\penglish}[1]{\colchunk{\begin{itemize}%[leftmargin=.3in]
\item[\arabic{parnum}]{#1}%
    \end{itemize}}\colplacechunks}
    
% command \textref{}{} automating references to label name + line number
\newcommand{\textref}[2]{\hyperref[\getrefnumber{#1}-par#2]{\nameref{#1}, line #2}}

% command \currentsecno returns current section (needed for automating references)
\makeatletter
\newcommand{\currentsecno}{%
  \ifnum\c@section=0 %
  \thechapter
  \else
  \ifnum\c@subsection=0 %
  \thesection
  \else
  \ifnum\c@subsubsection=0 %
  \thesubsection
  \else
  \thesubsubsection
  \fi
  \fi
  \fi
}


% INTERNAL / EXTERNAL LINK HANDLING
\usepackage{hyperref} % needs to be called as one of last packages but BEFORE polyglossia
\hypersetup{
    colorlinks=true,       % false: boxed links; true: colored links
%    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
%    citecolor=blue,        % color of links to bibliography
%    filecolor=magenta,      % color of file links
%    urlcolor=cyan           % color of external links
	allcolors=blue
}


% LANGUAGE / TEXT RENDERING SETUP
\usepackage{fontspec,xunicode}
\usepackage{polyglossia} % needs to be called as last package!

\setmainlanguage{english}
\setotherlanguage{arabic}

\setmainfont[Scale=1,Ligatures=TeX]{Linux Libertine O}
\newfontfamily\arabicfont[Script=Arabic,Scale=1.3]{Scheherazade}

\begin{document}

\section{Analysis}

This section is largely prose. Within the text, short segments of the source text(s) can be given in linguistic detail using \verb|gb4e| or another linguistics-oriented package:

\begin{exe}
\ex \label{ex:chad:}
\gll	 wa ʾabū saʾalā, gāl-a wēn al-hūtāy? \\
		 and father.\textsc{3msg.poss} ask.\textsc{3msg.pfv} say.\textsc{3msg.pfv} where \textsc{art}-fish\\
		\glt `the father asked him, he said ``where's the fish?'' (\textref{text:chad}{2})
\end{exe}

An internal hyperlink to the correct line in the longer text, below, is automatically generated with the macro \verb|\textref{text:chad}{2}|, where the first variable is the subsection label (manually added) and the second variable is the line being referenced.

\section{Texts}

\subsection{Chadian Narrative Text} \label{text:chad}

The following is a retranscription of a text from Roth (1979, pp. 226-228) with an English translation by the current author \ldots\

\begin{parcolumns}[colwidths={1=2 in},nofirstindent]{2}
%

\parabic{hāda, rāǧil hawwāti. maša hawwat, wa ligiyā, hūtāy, ǧābā fī bēt; wa antā lē wilēda. gāl ʾamšī, bīʾa.}
\penglish{There was this fisherman. He went and fished and caught one, a fish, he brought it to the house, and gave it to his son. He said ``go, sell it.'' }

\parabic{maša anta lē binēyt as-sultān. wa gabbal ǧāʾ wa ʾabū saʾalā, gāl-a wēn al-hūtāy? gāl yā abūyī (awūyi), al-hūtāy sirig.}
\penglish{[The son] went and gave it to the Sultan's daughter. When he'd returned the father him; he said ``where's the fish?'' He [the son] said ``Oh father, the fish was stolen.''}

\parabic{wa battan maša, hawwat, wa ǧabā hūtāy wāhid. wa anta lē wilēda. gāl ʾamši bīʾa wa maša, anta lē binēyt as-sultān.}
\penglish{So again he went, fished, an brought back another fish. And he gave it to his son. He said ``go sell it'' and [the son] went off, gave it to the Sultan's daughter.}

% additional lines are added with \parabic and \penglish

\setcounter{parnum}{0}
\leavevmode\refstepcounter{textID}
\end{parcolumns}


\end{document}
